Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-15 ms/ms.qmd
Fixes to wording

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).

>>>>

We downloaded metadata on the preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`). After removing `r dim(dupl)[1]` duplicate titles – suggesting a few authors created multiple submissons for the same preprint rather than simply updated an existing submission – we had data for a total of `r pr` preprints.
